### 2011-08-25 doc/theses/vitasek/chapter-4-experiments.tex
Thesis: in progress.

\begin{center}
\bigskip
\begin{tabular}{| l | l |}
  \hline
  \hline
  Machine           & TODO \\
  Input data        & all official and sized test data sets \\
  Iterations        & 50 \\
  Pool size         & not applicable \\
  $\alpha$, $\beta$ & not applicable \\
  \hline
\end{tabular}
\bigskip
\end{center}

@@

\begin{center}
\bigskip
\begin{tabular}{| l | l |}
  \hline
  \hline
  Machine           & TODO \\
  Input data set    & all official test data sets \\
  Iterations        & 50 \\
  Pool size         & 10 \\
  $\alpha$, $\beta$ & $1$, $1$ \\
  \hline
\end{tabular}
\bigskip
\end{center}

@@

\begin{center}
\bigskip
\begin{tabular}{| l | l |}
  \hline
  \hline
  Machine           & TODO \\
  Input data        & all official test data sets \\
  Iterations        & 20 \\
  Pool size         & 10 \\
  $\alpha$, $\beta$ & $1$, $1$ \\
  \hline
\end{tabular}
\bigskip
\end{center}

@@

TODO with the best construction heuristic, which IH is the best? Note that this needn't be the best combination!

>>>>

\begin{center}
\bigskip
\begin{tabular}{| l | l |}
  \hline
  \hline
  Machine           & Dual Core \\
  Input data        & all official and sized test data sets \\
  Iterations        & 50 \\
  Pool size         & not applicable \\
  $\alpha$, $\beta$ & not applicable \\
  \hline
\end{tabular}
\bigskip
\end{center}

@@

\begin{center}
\bigskip
\begin{tabular}{| l | l |}
  \hline
  \hline
  Machine           & Dual Core \\
  Input data set    & all official test data sets \\
  Iterations        & 50 \\
  Pool size         & 10 \\
  $\alpha$, $\beta$ & $1$, $1$ \\
  \hline
\end{tabular}
\bigskip
\end{center}

@@

\begin{center}
\bigskip
\begin{tabular}{| l | l |}
  \hline
  \hline
  Machine           & Quad Core \\
  Input data        & all official test data sets \\
  Iterations        & 20 \\
  Pool size         & 10 \\
  $\alpha$, $\beta$ & $1$, $1$ \\
  \hline
\end{tabular}
\bigskip
\end{center}

@@

%         NB class BestIHForGlpk

TODO with the best construction heuristic (GLPK), which IH is the best? Note that this needn't be the best combination!
